---
title: "18BCE080_PRAC8"
author: "Ishan Tewari"
date: "29/04/2021"
output: html_document
---


Loading the iris dataset:
```{r}
library(datasets)
data(iris)
summary(iris)
```


Checking the shape and feature names of the dataset:
```{r}
print("Shape of IRIS dataset")
dim(iris)
print("Features of IRIS dataset")
names(iris)
```


Exploring the structure of IRIS dataset.
```{r}
str(iris)
```


Exploring the entries of the dataset for 'virginica' species
```{r}
virginica = iris[iris['Species'] == "virginica", ]
head(virginica)
```

Finding the mean and standard deviation for 'sepal width' and 'sepal length' for each type of species.
```{r}
print("Mean of sepal length")
aggregate(x = iris$Sepal.Length,
          by = list(iris$Species),
          FUN = mean)
print("Standard deviation of sepal length")
aggregate(x = iris$Sepal.Length,
          by = list(iris$Species),
          FUN = sd)
print("Mean of sepal width")
aggregate(x = iris$Sepal.Width,
          by = list(iris$Species),
          FUN = mean)
print("Standard deviation of sepal width")
aggregate(x = iris$Sepal.Width,
          by = list(iris$Species),
          FUN = sd)
```

Plotting the histogram and box plot of 'sepal.length' variable.
```{r}
hist(iris$Sepal.Length, col = "skyblue", xlab = "Sepal Length", main = "Histogram of Sepal Length of Iris Dataset")
boxplot(Sepal.Length  ~ Species, iris, main = "Boxplot of Sepal Length of iris dataset", col = "lightpink3")
```
Plotting the histogram and box plot of 'petal.length' variable.
```{r}
hist(iris$Petal.Length, col = "skyblue", xlab = "Petal Length", main = "Histogram of Petal Length of Iris Dataset")
boxplot(Petal.Width  ~ Species, iris, main = "Boxplot of Petal Width of iris dataset", col = "lightpink3")
```

Plotting the correlation amongst the attributes in the dataset.
```{r}
library(corrplot)
corelation = cor(iris[, 1:4])
corrplot(corelation, method='circle')
```
Draw the pie chart for species attribute.
```{r}
table(iris$Species)
pie(table(iris$Species), main = "Pie Chart of the Iris data set Species",
    col = c("orange1", "chocolate", "coral"), radius = 1)
```

Export the plot created in one of the cells as a .png file.
```{r}
jpeg("prac8_1.jpg")
hist(iris$Sepal.Length, col = "skyblue", xlab = "Sepal Length", main = "Histogram of Sepal Length of Iris Dataset")
dev.off()
jpeg("prac8_2.jpg")
boxplot(Sepal.Length  ~ Species, iris, main = "Boxplot of Sepal Length of iris dataset", col = "lightpink3")
dev.off()
```
